Python to Assembly Compilation

### 2011-12-13 paper/paper.tex
changing to pdf instead of png
Add some valgrind results

\usepackage{amsmath}
\usepackage[pdftex]{graphicx}

@@

\includegraphics[scale=0.48]{compiler_flow.png}

@@

The compiler creates temporary variables in a number of situations (namely function calls and as a result of flattened expressions).  These temporary variables need not hang on to their memory reference past the next assignment to the actual result variable.

@@

The solution we took makes a slight modification to program behaviour, but we feel it is an acceptable trade-off.  In every scope, we add an immediate assignment as the first instructions.  This assignment is to a primitive, so it costs us no memory and then a decrement on the reference counter amounts to a function call with a no-op.  This function call overhead could potentially be avoided by adding code to check if the variable points to an object or a primitive and is a future enhancement for performance.

@@

An additional problem is lack of static single assignment.  When a variable is re-assigned to its own name, the code should decrement the reference counter on the previous version of the object and increment it on the new version.
\subsection{Assembly Output}
We modified the x86 assembly to include calls to set up our memory tracking system and print statistics at the end of the program.
\section{Results}
\subsection{Execution}
\subsection{Memory}
\section{Future work}
\section{Related Work}
\appendix
\section{Appendix Title}

>>>>

\usepackage{amsmath}
\usepackage[pdftex]{graphicx}
\usepackage{listings}

@@

\includegraphics[scale=0.48]{compiler_flow.pdf}

@@

The compiler creates temporary variables in a number of situations (namely function calls and as a result of flattened expressions).  These temporary variables need not hang on to their memory reference past the next assignment to the actual result variable.  Any temporary variable is dereferenced immediately at the end of the current scope if it is not the variable being returned.  If it is the return variable we ignore decrementing the reference on this variable, thereby assuring the caller that the object returned is correctly reference counted for its assignment.  If we had decremented the reference counter, due to the immediate nature of garbage collection, we would have been returning a value which did not point to an allocated memory region.

@@

The solution we took makes a slight modification to program behaviour, but we feel it is an acceptable trade-off.  In every scope, we add an immediate assignment as the first instructions.  This assignment is to a primitive, so the cost is minimal and then a decrement on the reference counter amounts to a function call with a no-op.  This function call overhead could potentially be avoided by adding code to check if the variable points to an object or a primitive and is a future enhancement for performance.  A program which used uninitialized (or declared) variables for program flow control would then have its runtime semantics changed.  We felt this was a sufficient trade off since such use of an exception for program flow control is frowned upon in practice and the benefit to our design was an obvious positive.

@@

\subsection{Assembly Output}
We modified the x86 assembly to include calls to set up our memory tracking system and print statistics at the end of the program.  Running analysis tools such as valgrind on our programs before and after shows the obvious gain of going from every memory allocation leaks to zero leaks.
\section{Results}
\subsection{Execution}
\subsection{Memory}
\subsubsection{Valgrind results}
For the trivial program
\begin{verbatim}
i = 0
list = []

while i !=  10000:
    list = list + [[i]]
    i = i + 1

\end{verbatim}
Without any garbage collection, valgrind reports 
\begin{verbatim}
==23467== LEAK SUMMARY:
==23467==    definitely lost: 560,028 bytes in 20,001 blocks
==23467==    indirectly lost: 199,004,992 bytes in 20,191 blocks
==23467==      possibly lost: 1,375,008 bytes in 19,810 blocks
\end{verbatim}
With our reference counting for the same program
\begin{verbatim}
==23831== LEAK SUMMARY:
==23831==    definitely lost: 0 bytes in 0 blocks
==23831==    indirectly lost: 0 bytes in 0 blocks
==23831==      possibly lost: 0 bytes in 0 blocks
\end{verbatim}
\section{Future work}
\section{Related Work}
\appendix
\section{Appendix Title}
